Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-10 Revision/manuscript.tex
feedback to comments

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past. Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models. \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses. \red{ I do not understand what the following means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days? How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?}) for the shock to take effect on the stock price. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. All the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$. As a result, we consider weighting with respect to  
  \begin{align*}
    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  \end{align*}
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$. \red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} The model $\mc{M}_2$ is then changed to 
  \begin{align*}
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
\end{array}
  \end{align*}
  where $\delta_i \in \R^{p \times 2}$. \red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?  It seems that, as currently written, $\alpha_i$ should be replaced by $\alpha_{i,t}$, for $t = T^*+1, T^*+2$, where it is understood that $\alpha_{i,T^*+1}$ is close to zero. But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all? What did you actually do here?}
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 15 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. We only include the last three Macbook releases in our donor pool because those releases are similar to the current release in the sense that Apple inc. has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019, apple2020}. %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

>>>>

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past. Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models. \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses. \red{Please clarify:...} \textcolor{blue}{Our shock effect of interest is similar to innovational  outliers  in the sense that it is an additive effect in the model of response only at a particular time point but it impacts the subsequent responses through an autoregressive structure.}

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days? \textcolor{blue}{It took two trading days for shock effects for 2017 and 2018 but 6 trading days for 2019.} How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?} \textcolor{blue}{We cannot know how long it took for the shock effect in 2020 to take an effect. From the past data (i.e., data in 2017 and 2018), I think 2 trading days are a safe guess.}) for the shock to take effect on the stock price. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. All the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$. As a result, we consider weighting with respect to  
    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$. \red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} \textcolor{blue}{In this case, $\mathcal{W}= \{\mathbf{W}\in [0,1]^n\colon 1_n'\mathbf{W}=1\}$ and we aim to find $\mathbf{W}^*\in \mathcal{W}$ with $\mathbf{W}^*=(w_2^*,\ldots, w_{n+1}^*)'$ such that }
    \textcolor{blue}{\mathbf{x}_{i, T_i^*+1:T_i^*+2}=\sum_{i=2}^{n+1}w_i^*\mathbf{x}_{i, T_i^*+1:T_i^*+2}}.
  \textcolor{blue}{and $\mathbf{W}^*$ is estimated by}
 \textcolor{blue}{\mathbf{W}^*= \argmin_{\mathbf{W}\in \mathcal{W}} \left\| \mathbf{x}_{i, T_i^*+1:T_i^*+2}-\sum_{i=2}^{n+1}w_i^*\mathbf{x}_{i, T_i^*+1:T_i^*+2} \right\|_{2p}.}
The model $\mc{M}_2$ is then changed to 
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \textcolor{red}{\alpha_i 1_2= \mu_{\alpha}1_2+\mbf{x}_{i, T_i^*+1:T_i^*+2}'\delta_{i}+ \t{\varepsilon}_{i}1_2},
\end{array}
  where \textcolor{red}{$\delta_i \in \R^{p \times 1}$ is not assumed to be random}. \red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?  It seems that, as currently written, $\alpha_i$ should be replaced by $\alpha_{i,t}$, for $t = T^*+1, T^*+2$, where it is understood that $\alpha_{i,T^*+1}$ is close to zero. But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all? What did you actually do here? \textcolor{blue}{I change the model accordingly where we cannot assume $\delta_i$ is random anymore in this context and it has to be particular $\delta_i$ such that the model holds. It is also possible that  we can use $\alpha_{i,t}$. By taking it two days to take effect, I mean $\alpha_{i, T_i^*+1}$ is small but not close to zero and it should be taken into consideration together with $\alpha_{i, T_i^*+2}$.  I personally prefer $\alpha_i$ instead of $\alpha_{i,t}$ since $\alpha_i$ is more intuitive  in that there is only one gross shock effect. Or, there is another possible approach. Recall that we can use different covariates in the model of $\alpha_i$  and in the model of $y_{i,t}$. So, we can only use $\mathbf{x}_{i, T_i^*+1}$ to construct the weights. Please let me know what you think and which model you prefer.}}
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 15 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. We only include the last three Macbook releases in our donor pool because those releases are similar to the current release in the sense that Apple inc. has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019, apple2020}. %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}
